% masthead here
\noindent Journal of Science \& Engineering (J S\&E) publishes high quality, peer-reviewed, original research, short articles, articles, letters, and reports by promising students of science and engineering.  J S\&E is a publication of the Freehold Regional High School District Press. Our online ISSN is 3066-7623 and our print ISSN is 3066-7607. Metadata and digital object identifiers (DOI) for all fulltext articles are registered with Crossref. Our primary aim is to highlight science and engineering original research done by secondary students. An ancillary goal is to teach science/engineering communication, technical writing, and the peer review process to secondary students. J S\&E is an open access journal.
\vspace{2ex}

%\masthead here
\noindent Our editorial office is located at:\\

\noindent Journal of Science \& Engineering\\20 Church Lane Room G201\\Englishtown, NJ 07726\\United States
\vspace{2ex}

\noindent\small Editorial board
\begin{itemize}
\itemsep-0.5em
\item[] B Anderson
\item[] C Bennett
\item[] E Cartaya
\item[] D Evangelista
\item[] E Kaplan
\item[] E Levin
\item[] V Oleksy
\item[] S Pepper
\item[] J Philhower
\item[] J Powers
\item[] K Suchodolski
\item[] L Stelljes
\end{itemize}

\noindent\small Advisory board
\begin{itemize}
\itemsep-0.5em
\item[] S Currie
\item[] A Brusotti
\item[] J Hein
\item[] M Venuto
\item[] C Provow
\item[] J Komitas
\end{itemize}

\vfill

\noindent{Copyright \copyright\ 2026 The Journal of Science and Engineering. This work is licensed under CC BY-NC 4.0. To view a copy of this license, visit \url{https://creativecommons.org/licenses/by-nc/4.0/}}
\vspace{2ex}

\noindent{\url{https://manalapan.frhsd.com/}}
\vspace{2ex}

\noindent{\url{https://sites.google.com/frhsd.com/seopenhouse/home}}
\vspace{2ex}
